Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-10 Response to reviewers.tex

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#3}

\noindent \emph{There are several concerns should be considered.}\\

\noindent (1) \emph{In section introduction, this manuscript should describe the contribution of this work. }

\begin{verbatim}
The reviewer is right. The main contribution of this paper to the 
state of the art was not properly described. Thus, as stated above 
in the second response to Reviewer #2, we have clarified this in 
the introduction improving some paragraphs and adding new sentences 
(see page 2, second column):

@@

With these issues in mind, in this paper, we firstly present an 
analysis on a real dataset, provided by the Spanish publishing company 
Trevenque Editorial S.L.
This study has been conducted by means of data mining and visualisation
 techniques. Then, a feature selection process is performed using three
 different methods, in order to find out what are the relevant variables
 describing a book  in the prediction, or estimation, procedure. 
This procedure is performed by applying a set of regression algorithms 
to the different datasets (those with a different number of variables), 
yielding a set of models which could be used as the desired tool.

Given this, the main contribution of this paper to the state of the art 
is the development of the aforementioned methodology to process book sales 
data, in which: firstly, the most relevant variables are identified, and then,
 these variables are considered to `refine' the data in order to conduct
 accurate predictions on future sales. To our knowledge this is the first 
work in which regression methods have been applied to estimate sales for 
new launched books. Moreover, as stated before, we have used in the study 
a real dataset of book sales (related to the Spanish market), which is 
another point to remark."
\end{verbatim}

~\\
\noindent (2) \emph{sections 4.1 and 4.2 should be moved to section 2. }

\begin{verbatim}
We appreciate the reviewer's suggestion, however, considering that those 
sections describe methods and metrics used in the state of the art, 
our aim was to make the Section 2 as independent as possible from the rest, 
given that it is a key section on every work.

@@

The authors think that `mixing' background concepts there could mean, 
somehow, a lost in quality for that section.

In addition, we also guess that if those subsections would be moved 
to Section 2, maybe Section 4.3 should be moved too, as it also describes 
some background concepts (usual evaluation metrics). Thus, the methodology 
section would be certainly quite short and incomplete.

@@

Finally, the rest of the reviewers haven't requested to change the 
organisation and, moreover, Reviewer #2 has remarked that the paper 
is well organized in his/her last comment.

For these reasons we have decided to maintain those subsections as part
of the methodology (section 4).

We hope that the reviewer agrees with this decision.
\end{verbatim}

@@

~\\
\noindent (3) \emph{In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it. }

\begin{verbatim}
Taking into account the reviewer's comment, we have improved the 
description of the methodology including a flowchart (see Figure 1 
at page 6).

Every step/stage shown in that figure has been described in the 
following paragraphs (Section 4, page 6).
\end{verbatim}

@@

~\\
\noindent (4) \emph{In Section 5, parameter settings of 
M5P, kNN and RF also should be shown. }

\begin{verbatim}
In agreement with reviewer’s comment, Section 5 has been improved, 
including the parameter settings of M5P, kNN and RF methods (see 
Subsection 5.1, page 11, first column), along with the configuration 
parameters for the rest of methods.

The authors want to express our gratitude to this reviewer 
for his/her valuable comments and suggestions.
\end{verbatim}

### 2016-09-10 Response to reviewers.tex

This has been clarified in the text with the following sentence, at 
the end of section 5.2 (page 12, second column):

"It is important to note that both RF and M5P have an embedded feature 
selection mechanism (the variables which compose the final trees), 
however this is part of their inherent procedure. In the following 
section we will apply three filter-based feature selection techniques 
on the dataset, so all the methods will profit."
\end{verbatim}

~\\
\noindent (4) \emph{It seems more reasonable to organize and write that paper according to regression viewpoint only. }

\begin{verbatim}
In agreement with reviewer's comment, we have revised the whole paper 
remarking the regression topic present on the work. We have clarified 
in several paragraphs along the text that the problem has been 
addressed by means of regression methods (for instance, note the new 
title of Section 4.2), or we have generally referred to the term 
'regression' instead of 'classification', in order to better suit 
the regression viewpoint.

@@

\begin{verbatim}
Following reviewer's suggestion, all the results tables have been 
moved to the Appendix and that data has been summarized and 
presented as the new Figures 2, 4, 5 and 6 (in Subsection 5.2 and 
Section 6) in order to make that numeric data clearer and to improve 
their comprehension.

Their analysis has been also changed and improved considering Figures 
instead of tables.
\end{verbatim}

~\\
\noindent (5) \emph{Graphical abstract should be added. This paper is organized well. The authors should revise their work according to above comments. }

\begin{verbatim}
In agreement with reviewer's suggestion, we have designed (and 
uploaded) a graphical abstract as a visual summary of the paper 
structure and the utility of the obtained results.

@@

Given this, the main contribution of this paper to the state of the art 
is the development of the aforementioned methodology to process book sales 
data, in which: firstly, the most relevant variables are identified, and then,
these variables are considered to `refine' the data in order to conduct
accurate predictions on future sales. To our knowledge this is the first 
work in which regression methods have been applied to estimate sales for 
new launched books. Moreover, as stated before, we have used in the study 
a real dataset of book sales (related to the Spanish market), which is 
another point to remark."
\end{verbatim}

~\\
\noindent (2) \emph{sections 4.1 and 4.2 should be moved to section 2. }

\begin{verbatim}
We appreciate the reviewer's suggestion, however, considering that those 
sections describe methods and metrics used in the state of the art, 
our aim was to make the Section 2 as independent as possible from the rest, 
given that it is a key section on every work.

The authors think that 'mixing' background concepts there could mean, 
somehow, a lost in quality for that section.

@@

\begin{verbatim}
Taking into account the reviewer's comment, we have improved the 
description of the methodology including a flowchart (see Figure 1 
at page 6).

Every step/stage shown in that figure has been described in the 
following paragraphs (Section 4, page 6).
\end{verbatim}

~\\
\noindent (4) \emph{In Section 5, parameter settings of 
M5P, kNN and RF also should be shown. }

\begin{verbatim}
In agreement with reviewer's comment, Section 5 has been improved, 
including the parameter settings of M5P, kNN and RF methods (see 
Subsection 5.1, page 11, first column), along with the configuration 
parameters for the rest of methods.
